Parallel algorithm for solving multicriterial optimization problems using elements of machine learning

### 2025-04-06 2025/RSCD_MCO/RSD-2025.tex
MCO 2025 рисунки

>>>>

\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{fig1.png}
\caption{Computational scheme of the algorithm for solving multicriterial optimization problems using machine learning models.} \label{fig1}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{fig2.png}
\caption{Example of Pareto set evaluation in solving two scalar optimization problems.} \label{fig2}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.8\textwidth]{fig3.png}
\caption{Neural network models used to calculate the characteristic $R_{PS}(i)$.} \label{fig3}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{fig4.png}
\caption{Examples of Pareto set evaluation for the case of two scalar optimization problems.} \label{fig4}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.8\textwidth]{fig5.png}
\caption{Comparison of HW index values for sequential algorithm implementation.} \label{fig5}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.8\textwidth]{fig6.png}
\caption{Dependence of the mean value of the index HW from the trial number per process for the case of 20 processes.} \label{fig6}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.8\textwidth]{fig7.png}
\caption{Dependence of the HW index on the number of trials executed for different number of processes.} \label{fig7}
\end{figure}
